---
title: 'DS 202 - Homework #6'
author: "Mike Zaino mzaino16"
date: "4/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(tidyverse)
```

## Top dogs

In this homework, you will try to reproduce the fantastic infographic for [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/), originally produced by David McCandless. The raw data can be found [here](https://docs.google.com/spreadsheets/d/1l_HfF5EaN-QgnLc2UYdCc7L2CVrk0p3VdGB1godOyhk/edit#gid=10). You can download this file by File -- Download As -- Microsoft Excel (.xlsx).

**Submission instructions**: Create a folder named `ds202_hw6`, and name the RMarkDown file including your solutions `hw6.Rmd` under this folder. For the submission, create a GitHub repository named `ds202_hw6` under your GitHub account, and push both `hw6.Rmd` and the knitted `hw6.html` before the deadline. I will assume you use the same GitHub username as for your HW5 submission. The latest version of your homework appearing on GitHub before the deadline is graded. *It is crucial to follow the exact folder structure and file names*, so that your homework can be reproduced and graded by an automated script. This homework is **due on April 22** before class.

1. Import the data and clean appropriately. To read in the data, you can use `readxl::read_xlsx('fileNameHere', sheet='sheetNameHere')`. Required data are in the sheets `Best in show` and `Best in show full sheet`. Take extra care on the column names and the first few rows of the data frame after read in.

```{r, warning=FALSE, message=FALSE}
best <- readxl::read_xlsx('/Users/TheemikezanilyMac/Documents/School/DS 202/ds202_hw6/dogs.xlsx', sheet='Best in show')
bestfull <- readxl::read_xlsx('/Users/TheemikezanilyMac/Documents/School/DS 202/ds202_hw6/dogs.xlsx', sheet='Best in show full sheet')

best2 <- best[-c(1,2,3,4,6),c(1,5,7,9,10,14,17,18,21,23,24,25,28,31,32,33,34,35,43,44,46,48)]
names(best2) <- best2[c(1),]
best2 <- best2[-c(1),]

bestfull2 <- bestfull[-c(1,3),-c(2,4,6,10,25,31,37,38,39,40,47,48,49,62,72,73,74,75)]
names(bestfull2) <- bestfull2[c(1),]

bestfull3 <- bestfull2[-c(1),]
bestfull4 <- bestfull3 %>% 
  filter(!is.na(`datadog score`)) %>%
  filter(!is.na(`POPULARITY IN US`)) %>% 
  filter(!is.na(`intelligence category`)) %>% 
  mutate(`datadog score` = as.numeric(`datadog score`),
         `POPULARITY IN US` = as.numeric(`POPULARITY IN US`),
         `Sources - see bottom right` = as.factor(`Sources - see bottom right`),
         `category` = as.factor(`category`),
         `size category` = as.factor(`size category`),
         `intelligence category` = as.factor(`intelligence category`),
         `value` = ifelse(`intelligence category` %in% c('Brightest', 'Excellent', 'Above average'), 'clever',
                ifelse(`intelligence category` %in% c('Average', 'Fair', 'Lowest', 'no data'), 'dumb', 'dumb')),
         `size category` = factor(`size category`, levels= c('small', 'medium', 'large')))
```

2. Create a graphics similar to the  [top dogs](https://informationisbeautiful.net/visualizations/best-in-show-whats-the-top-data-dog/) figure. Your figure needs to display the following information with appropriate plotting elements:

- breed of dog
- type of dog (work, toy, etc.)
- size of dog
- data score 
- popularity
- intelligence of the dog
- appropriate legends & explanation

```{r}
bestfull4 %>% 
  ggplot(aes(x=`datadog score`, y=`POPULARITY IN US`, color=`category`, shape = `value`))+
  geom_point(aes(size=`size category`)) + 
  scale_y_reverse() + theme_classic() + geom_vline(xintercept = 2.4) + geom_hline(yintercept = 60)+
  geom_text(aes(label=`Sources - see bottom right`), size=2.5, nudge_y = -2) + 
  labs(size = 'Size', x = 'Data Score', y= 'Popularity', color = 'Type', shape = 'Intelligence', title ='Best in Show: The Ultimate Data Dog') + 
  annotate("text", x = 1.3, y = 0, label = "Inexplicably Overrated") + 
  annotate("text", x = 3.5, y = 0, label = "Hot Dogs!") + 
  annotate("text", x = 1.3, y = 90, label = "The Rightly Ignored") + 
  annotate("text", x = 3.3, y = 90, label = "Overlooked Treasures")
```

Hints and Notes:

- The breed of dog can be displayed without the silhouttes (text only is fine)
- Avoid (too much) overlaps!
- Choose a good color scheme.
- Your submission is supposed to be fully reproducible, i.e. the TA and I will 'knit' your submission in RStudio. 